Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-23 Multiresolution_framework/ltx/ResubmissionLetter.tex
Revised version submitted to NeuroImage

% \emph{Please explain why this manuscript is suitable for publication in PLoS Computational Biology; why will your paper inspire the other members of your field, and how will it drive research forward?}

I am writing to seek publication of our research article titled `Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model' in Neuroimage.

The novel aspects of this paper include:
\begin{itemize}
	\item a multi-resolution model-based, data-driven estimator of continuum neural field parameters ;
	\item simultaneous representation of both the macroscopic and microscopic dynamics of the system ;
	\item a derivation of an algorithm for estimating intracortical connectivity with an arbitrary shape using the Amari type neural field equations.
\end{itemize}

>>>>

    We thank the reviewers for their encouraging comments and their contribution to improving this paper. Please find below our responses to the reviewers questions and suggestions regarding the manuscript. 
\\
